Low prevalence of \emph{a priori} power analyses in motor behavior research

### 2022-07-12 docs/preprint/preprint.tex
init

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man, donotrepeattitle,mask,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Metascience, Sample size planning, Positivity rates, Effect size}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{setspace}
\usepackage{censor}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 2, 2, 3, 3, 2, 2, 1]{Brad McKay, Abbey Corson, Mary-Anne Vinh, Gianna Jeyarajan, Chitrini Tandon, Hugh Brooks, Julie Hubley, Michael J. Carter\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {School of Human Kinetics, University of Ottawa}, {School of Interdisciplinary Sciences, McMaster University}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Low prevalence of a priori power analyses in motor behavior research},
  pdflang={en-EN},
  pdfkeywords={Metascience, Sample size planning, Positivity rates, Effect size},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
\emph{A priori} power analyses can ensure studies are unlikely to miss interesting effects. Recent metascience has suggested that kinesiology research may be underpowered and selectively reported. Here, we examined whether power analyses are being used to ensure informative studies in motor behavior. We reviewed every article published in three motor behavior journals between January 2019 and June 2021. Power analyses were reported in 13\% of studies (\emph{k} = 636) that tested a hypothesis. No study targeted the smallest effect size of interest. Most studies with a power analysis relied on estimates from previous experiments, pilot studies, or benchmarks to determine the effect size of interest. Studies without a power analysis reported support for their main hypothesis 85\% of the time, while studies with a power analysis found support 76\% of the time. The median sample sizes were \emph{n} = 17.5 without a power analysis and \emph{n} = 16 with a power analysis, suggesting the typical study design was underpowered for all but the largest plausible effect size. At present, power analyses are not being used to optimize the informativeness of motor behavior research. Adoption of this widely recommended practice may greatly enhance the credibility of the motor behavior literature.
}

@@

@@

\caption{\label{tab:table1}Elements of the data extraction process and the corresponding action the researchers performed.}
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{21em}>{\raggedright\arraybackslash}p{20em}}
\toprule
Item & Action\\
\midrule
1. Did the study meet the inclusion criteria? & Yes or No, and provide reason.\\
\addlinespace
2. Did the authors report a power analysis? & Yes or No.\\
\addlinespace
3. Hypothesis quote. & Copy pasted quote of the hypotheses.\\
\addlinespace
4. Results quote. & Copy pasted quote of the results interpretation\\
\addlinespace
5. Did the authors conclude support for any of the main hypotheses? & Yes or No.\\
\addlinespace
6. Sample size. & Calculate average per group.\\
\addlinespace
7. Power analysis effect type. & Select from a list.\\
\addlinespace
8. Power analysis effect estimate. & Report the effect size used for the analysis.\\
\addlinespace
9. Power analysis effect converted to Cohen's d. & Perform conversion whenever possible.\\
\addlinespace
10. Effect size justification. & Select from a list.\\
\addlinespace
11. Power estimate from the power analysis. & Report value.\\
\bottomrule
\end{tabular}
\end{table}

@@

\vspace{5ex}

@@

\noindent The preregistration, data, and scripts can be accessed here: \url{https://osf.io/wsdpv/}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  doc, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Metascience, Sample size planning, Positivity rates, Effect size
\newline \newline \hspace*{\fill} \textcolor{orange}{\textbf{\emph{PREPRINT - NOT PEER-REVIEWED}}} \hspace*{\fill}
\newline \newline \emph{Please cite as}: McKay, B., Corson, A., Vinh, MA., Jeyarajan, G., Tandon, C., Brooks, H., Hubley, J., \& Carter, M.J. (2022). Low prevalence of a priori power analyses in motor behavior research. \emph{SportR$\chi$iv}
}
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{setspace}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 2, 2, 3, 3, 2, 2, 1]{Brad McKay, Abbey Corson, Mary-Anne Vinh, Gianna Jeyarajan, Chitrini Tandon, Hugh Brooks, Julie Hubley, Michael J. Carter\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {School of Human Kinetics, University of Ottawa}, {School of Interdisciplinary Sciences, McMaster University}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Low prevalence of a priori power analyses in motor behavior research},
  pdflang={en-EN},
  pdfkeywords={Metascience, Sample size planning, Positivity rates, Effect size
\newline \newline \hspace*{\fill} \textcolor{orange}{\textbf{\emph{PREPRINT - NOT PEER-REVIEWED}}} \hspace*{\fill}
\newline \newline \emph{Please cite as}: McKay, B., Corson, A., Vinh, MA., Jeyarajan, G., Tandon, C., Brooks, H., Hubley, J., \& Carter, M.J. (2022). Low prevalence of a priori power analyses in motor behavior research. \emph{SportR$\chi$iv}},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
\emph{A priori} power analyses can be used to ensure studies are unlikely to miss interesting effects. Recent metascience has suggested that kinesiology research may be underpowered and selectively reported. Here, we examined whether power analyses were currently being leveraged to ensure informative studies in the motor behavior research. We reviewed every article published in the \emph{Journal of Motor Learning and Development}, the \emph{Journal of Motor Behavior}, and \emph{Human Movement Science} between January 2019 and June 2021. Our results revealed that power analyses were reported in 13\% of all studies (\emph{k} = 636) that tested a hypothesis. Yet, no study in the sample targeted the smallest effect size of interest. Most studies with a power analysis instead relied on estimates from previous studies, pilot studies, or benchmarks to determine the effect size of interest. Studies in this sample without a power analysis reported support for their main hypothesis 85\% of the time, while studies with a power analysis found support 76\% of the time. The median sample sizes were \emph{n} = 17.5 without a power analysis and \emph{n} = 16 with a power analysis, suggesting the typical study design in our sample was underpowered for all but the largest plausible effect size. At present, power analyses are not being used to optimize the informativeness of motor behavior studies; a trend that likely extends to other kinesiology subdisciplines. Adoption of this simple and widely recommended practice may greatly enhance the credibility of the motor behavior literature and kinesiology research in general.
}

@@

\caption{\label{tab:table1}Elements of the data extraction process and the corresponding action the researchers performed.}
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{21em}>{\raggedright\arraybackslash}p{20em}}
\toprule
Item & Action\\
\midrule
1. Did the study meet the inclusion criteria? & Yes or No, and provide reason.\\
\addlinespace
2. Did the authors report a power analysis? & Yes or No.\\
\addlinespace
3. Hypothesis quote. & Copy pasted quote of the hypotheses.\\
\addlinespace
4. Results quote. & Copy pasted quote of the results interpretation\\
\addlinespace
5. Did the authors conclude support for any of the main hypotheses? & Yes or No.\\
\addlinespace
6. Sample size. & Calculate average per group.\\
\addlinespace
7. Power analysis effect type. & Select from a list.\\
\addlinespace
8. Power analysis effect estimate. & Report the effect size used for the analysis.\\
\addlinespace
9. Power analysis effect converted to Cohen's d. & Perform conversion whenever possible.\\
\addlinespace
10. Effect size justification. & Select from a list.\\
\addlinespace
11. Power estimate from the power analysis. & Report value.\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\hypertarget{author-contributions-credit-taxonomy}{%
\subsection{Author Contributions (CRediT Taxonomy)}\label{author-contributions-credit-taxonomy}}

\noindent Conceptualization: BM, MJC\\
Data curation: BM, MJC\\
Formal analysis: BM\\
Funding acquisition: MJC\\
Investigation: BM, AC, MV, GJ, CT, HB, JH\\
Methodology: BM, MJC\\
Project administration: BM, MJC\\
Software: BM, MJC\\
Supervision: BM, MJC\\
Validation: BM, MJC\\
Visualization: BM, MJC\\
Writing -- original draft: BM, AC, MV, GJ, CT, HB, JH, MJC\\
Writing -- review \& editing: BM, AC, MV, GJ, CT, HB, JH, MJC

@@

\noindent The preregistration, data, and scripts can be accessed using either of the following links: \url{https://osf.io/wsdpv/} or \url{https://github.com/cartermaclab/proj_power-motor-behavior}.

### 2022-07-12 docs/submission/submission.Rmd
init

abstract: |
  *A priori* power analyses can be used to ensure studies are unlikely to miss interesting effects. Recent metascience has suggested that kinesiology research may be underpowered and selectively reported. Here, we examined whether power analyses were currently being leveraged to ensure informative studies in the motor behavior research. We reviewed every article published in the *Journal of Motor Learning and Development*, the *Journal of Motor Behavior*, and *Human Movement Science* between January 2019 and June 2021. Our results revealed that power analyses were reported in 13% of all studies (*k* = 636) that tested a hypothesis. Yet, no study in the sample targeted the smallest effect size of interest. Most studies with a power analysis instead relied on estimates from previous studies, pilot studies, or benchmarks to determine the effect size of interest. Studies in this sample without a power analysis reported support for their main hypothesis 85% of the time, while studies with a power analysis found support 76% of the time. The median sample sizes were *n* = 17.5 without a power analysis and *n* = 16 with a power analysis, suggesting the typical study design in our sample was underpowered for all but the largest plausible effect size. At present, power analyses are not being used to optimize the informativeness of motor behavior studies; a trend that likely extends to other kinesiology subdisciplines. Adoption of this simple and widely recommended practice may greatly enhance the credibility of the motor behavior literature and kinesiology research in general.

keywords          : |
  Metascience, Sample size planning, Positivity rates, Effect size
  \newline \newline \hspace*{\fill} \textcolor{orange}{\textbf{\emph{PREPRINT - NOT PEER-REVIEWED}}} \hspace*{\fill}
  \newline \newline \emph{Please cite as}: McKay, B., Corson, A., Vinh, MA., Jeyarajan, G., Tandon, C., Brooks, H., Hubley, J., \& Carter, M.J. (2022). Low prevalence of a priori power analyses in motor behavior research. \emph{SportR$\chi$iv}
#wordcount         : ""

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "doc, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
 # - \pagewiselinenumbers
  - \raggedbottom

@@

kbl(table1,
    booktabs = TRUE,
    escape = TRUE,
    linesep = "\\addlinespace",
    caption = "Elements of the data extraction process and the corresponding action the researchers performed.",
    col.names = c("Item",
                  "Action")
    ) %>% 
  kable_styling(position = "left",
                font_size = 10) %>% 
  column_spec(1, width = "21em") %>% 
  column_spec(2, width = "20em")
```

@@

@@

## Author Contributions (CRediT Taxonomy)

\noindent Conceptualization: BM, MJC  
Data curation: BM, MJC  
Formal analysis: BM  
Funding acquisition: MJC  
Investigation: BM, AC, MV, GJ, CT, HB, JH  
Methodology: BM, MJC  
Project administration: BM, MJC  
Software: BM, MJC  
Supervision: BM, MJC  
Validation: BM, MJC  
Visualization: BM, MJC  
Writing -- original draft: BM, AC, MV, GJ, CT, HB, JH, MJC  
Writing -- review & editing: BM, AC, MV, GJ, CT, HB, JH, MJC

@@

## Open Science Practices
\noindent The preregistration, data, and scripts can be accessed using either of the following links: https://osf.io/wsdpv/ or https://github.com/cartermaclab/proj_power-motor-behavior.

>>>>

abstract: |
  *A priori* power analyses can ensure studies are unlikely to miss interesting effects. Recent metascience has suggested that kinesiology research may be underpowered and selectively reported. Here, we examined whether power analyses are being used to ensure informative studies in motor behavior. We reviewed every article published in three motor behavior journals between January 2019 and June 2021. Power analyses were reported in 13% of studies (*k* = 636) that tested a hypothesis. No study targeted the smallest effect size of interest. Most studies with a power analysis relied on estimates from previous experiments, pilot studies, or benchmarks to determine the effect size of interest. Studies without a power analysis reported support for their main hypothesis 85% of the time, while studies with a power analysis found support 76% of the time. The median sample sizes were *n* = 17.5 without a power analysis and *n* = 16 with a power analysis, suggesting the typical study design was underpowered for all but the largest plausible effect size. At present, power analyses are not being used to optimize the informativeness of motor behavior research. Adoption of this widely recommended practice may greatly enhance the credibility of the motor behavior literature.

keywords          : "Metascience, Sample size planning, Positivity rates, Effect size"
#wordcount         : ""

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
  - \usepackage{censor}
 # - \pagewiselinenumbers
  - \raggedbottom

@@

@@

kbl(table1,
    booktabs = TRUE,
    escape = TRUE,
    linesep = "\\addlinespace",
    caption = "Elements of the data extraction process and the corresponding action the researchers performed.",
    col.names = c("Item",
                  "Action")
) %>% 
  kable_styling(position = "left",
                font_size = 11) %>% 
  column_spec(1, width = "21em") %>% 
  column_spec(2, width = "20em")
```

@@

\vspace{5ex}

<!-- ## Author Contributions (CRediT Taxonomy) -->

<!-- \noindent Conceptualization: BM, MJC   -->
<!-- \noindent Data curation: BM, MJC   -->
<!-- \noindent Formal analysis: BM   -->
<!-- \noindent Funding acquisition: MJC   -->
<!-- \noindent Investigation: BM, AC, MV, GJ, CT, HB, JH   -->
<!-- \noindent Methodology: BM, MJC   -->
<!-- \noindent Project administration: BM, MJC   -->
<!-- \noindent Software: BM, MJC   -->
<!-- \noindent Supervision: BM, MJC   -->
<!-- \noindent Validation: BM, MJC   -->
<!-- \noindent Visualization: BM, MJC   -->
<!-- \noindent Writing -- original draft: BM, AC, MV, GJ, CT, HB, JH, MJC   -->
<!-- \noindent Writing -- review & editing: BM, AC, MV, GJ, CT, HB, JH, MJC -->

@@

## Open Science Practices
\noindent The preregistration, data, and scripts can be accessed here: https://osf.io/wsdpv/.
